О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-09 pps-linear-bound/pps-linear-lower-bound.tex
Cosmetics

\section{Introduction.}
Let $\mathbb{N}$ be the set of all positive integers and let $|M_1 - M_2|$ denote the Euclidean distance
between points $M_1$ and $M_2$ in a finite-dimensional space $\mathbb{R}^m$.
An \textit{integral point set} in $m$-dimensional Euclidean space is such a point set $M$ that all the distances between the
points of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
Erd\"os and Anning proved~\cite{anning1945integral,erdos1945integral} that every integral point set consists of a finite number of points.
Taking the fact into account, we will denote the set of all integral point sets of $n$ points in $m$-dimensional Euclidean space with
$\mathfrak{M}(m,n)$ (following the notation of~\cite{our-vmmsh-2018}).
The symbol $|M|$ will be used for cardinality of $M$, i.e. the quantity of points in $M$ in our case.

@@

\section{Lower bound for the diameter.}

@@

For $m \geq 3$, hypothesis 3.1 can be easily proved:
indeed, we can just take a facher integral point set according to construction 1
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex with proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all the points $M_J$ and still have points $H_{1,2}$ with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is irreducible.

>>>>

\section{Introduction}
Let $\mathbb{N}$ be the set of all positive integers and let $|M_1 - M_2|$ denote the Euclidean distance
between points $M_1$ and $M_2$ in a finite-dimensional space $\mathbb{R}^m$.
An \textit{integral point set} in $m$-dimensional Euclidean space is such a point set $M$ that all the distances between the
points of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
Erd\"os and Anning proved~\cite{anning1945integral,erdos1945integral} that every integral point set consists of a finite number of points.
Taking the fact into account, we will denote the set of all integral point sets of $n$ points in $m$-dimensional Euclidean space with
$\mathfrak{M}(m,n)$ (following the notation of~\cite{our-vmmsh-2018}).
The symbol $|M|$ will be used for cardinality of $M$, i.e. the quantity of points in $M$ in our case.

@@

\section{Lower bound for the diameter}

@@

For $m \geq 3$, hypothesis 3.1 can be easily proved:
indeed, we can just take a facher integral point set according to construction 1
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex with proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all the points $M_J$ and still have points $H_{1,2}$ with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is irreducible.
